\documentclass{letter}
\usepackage{hyperref}
\signature{Lucas}
\address{140 Riverside Dr \\ New York, NY \\ (and definitely not the subway)}
\begin{document}

\begin{letter}{Lord save my soul from \\ computer science, deep saints \\ of paper spirit.}
\opening{Gracelynne,}

Happy Birthday! I hope you'll recover quickly enough from the shock and 
disgust of a birthday card written in LaTeX to endure two paragraphs of 
my aggrandizing stupid jokes.

This past year has been downright explosive, and I don't think I've ever been prouder to be your friend.
When all your struggle came to a head, you held fast to your goals and
so much of it paid off this spring -- you're brilliant and interesting
and honestly, if anyone had continued to ignore that, it would've been
a legitimate travesty.

I know we haven't had the chance to speak as much this year, but I'm so
proud of everything you've accomplished and the things you've discovered
and maintained in yourself. As always, you're pulling wild talents and
interests out of your back pocket and going places so much bigger and
more significant than I could ever imagine -- if you don't keep doing 
what you're doing I'll be personally offended.

I remember last year when you told me it was crazy to imagine anyone 
could live in New York. Now you're replacing BTS biases with peers 
Fresh Off the Boat (so sorry), traveling all across the country and
outside of it, and making valedictorian speeches (at a graduation that
was legitimately ten times bigger than mine) -- honestly, Manhattan 
quant culture needs you so much more than you'll ever need it.

I know you'll keep doing great and I love you so much.

\closing{Wishing you the strength of tax filing,

your twin from another dumpster bin,}


\end{letter}
\end{document}